Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-11-02 VMCAI-revised-version/final.tex
up

>>>>

Recall that on the other end {\sc Resilience} is decidable for reset-VASS when $\Safe = \mathop{\uparrow} \Safe$ by Theorem~\ref{xxx}.
This suggests that the undecidability of {\sc State-resilience} 
comes more from the fact $\post^*(s_0)$ is not constructible~\cite{dufourd1998reset} in reset-VASS rather than from the difficulties inherent in searching for paths from $\post^*(s_0)$ to $\Safe$.  \nocite{mayr1998lossy}
\mathieu{À relire encore}
